# Animated graph



## Data cleaning

I want to find out the studios that is above the lower quartile of average rating to see its rating change across 1958 to 2020. 
Thus, further data cleaning is needed.
```{r, message=FALSE, results='hide'}

summary(studiotop50$rating)

studiotop37r <- studiotop50 %>% 
  arrange(desc(rating)) %>% 
#after looking at the code, find out how many is below the 2.75 lower quartile
  slice (1:37)

#create a data set that contains only anime starting year, rating of the anime, and the name of the anime.
selectstudio <- anime1 %>% select(title, startYr, studios, rating)

selectstudioall <- merge(studiotop37r, selectstudio,by = "studios", all = TRUE)

#clean all the NA
selectstudioclean <- na.omit(selectstudioall)
#re name the heading
colnames(selectstudioclean) <- c("studios", "production","avg_rating","title","startyr","rating")

#create a list that is showing the studios average rating of each year.
newavg <- selectstudioclean %>% select(studios, rating, production, avg_rating,startyr)
newavg1 <- aggregate(newavg[, 2:4], list(newavg$studios, newavg$startyr), mean)
colnames(newavg1) <- c("studios","startyr","rating", "production","avg_rating")
```

## Racing plot 1
This racing plot could show each year, which studio has highest average rating.
```{r, warning=FALSE,message=FALSE}

summary(selectstudioclean)
library(gganimate)
library(av)
#create ranking list
newavg2 <- newavg1 %>% group_by(startyr)%>% 
  arrange(startyr, - rating)%>% 
  mutate(ranking = 1:n())

#Drop row that the year is above 2020.
newavg2 <-newavg2 [!(newavg2$startyr == "2021"|newavg2$startyr == "2022"),]

#Plot the graph
top1 <- ggplot(newavg2, aes(ranking, group = studios, 
                fill = as.factor(studios), color = as.factor(studios))) +
  geom_tile(aes(y = rating,
                height = rating,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(studios, " ")), vjust = 0.5, hjust = 0.5, size = 6, fontface="bold") +
  geom_text(aes(y=rating,label = round(rating, digits = 1)), colour = "black", hjust=1) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
#reverse display
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
#set up theme i.e. the backgroud of the plot, the grid line etc
   theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=1),
        plot.subtitle=element_text(size=17, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"),
       plot.tag.position = c (0.2, 0)) 

#animate the graph with label
anim = top1 + transition_states(startyr, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Studio average rating change by year : {closest_state}',  
       subtitle  =  "Top 37 Studio racing plot", tag = "Figure4: 1958-2020 Studio's raced rating change")

#nframes = 2 x length of the showing year (startyr). Without setting the plot will only show first 50 years
anime.gif <- animate(anim, nframes = 150, fps = 2.5, width = 1000, height = 1200)
anime.gif
```


## Racing plot 2
This plot fixing each studio’s position for better look or target a specific studio to visualise the rating change over the years.
```{r, warning=FALSE,message=FALSE}

topcompany <- ggplot(data=newavg2,aes (x = studios, y = rating, fill = rating))+
  geom_bar(stat = 'identity',size = 6, fontface="bold")+ 
  geom_text(aes(label=format(round(rating)), y=rating, hjust = -1),
            position=position_dodge(1)) + coord_flip()+
  #Let the colour change along with the rating
  scale_fill_gradient(low = 'grey39', high = 'cyan')+
  scale_y_continuous("rating") + theme_classic()+
  #Set up theme
  theme(legend.position='none', axis.text.y = element_text(size = 10, face = "bold"),
        plot.subtitle = element_text(size = 15, hjust = 1, vjust = -2, face = "bold"),
        plot.tag.position = c (0.3, 0))+
  #Animate the graph
  transition_states(states=startyr, transition_length=4, state_length = 1) +
  ease_aes('cubic-in-out') + labs (subtitle = 'Year:{closest_state}',
                                   tag = "Figure5: 1958-2020 Studio's rating change")+
  labs(x='Studio name')

anime1.gif <- animate (topcompany, nframes = 150, fps = 2, width = 600, height = 800)
anime1.gif

```

## Racing plot on best studio

Merge data set first
```{r,warning=FALSE,message=FALSE}
#created a new dataset that merge top37 to the best studio
beststudior <- merge(newavg2, beststudio1, by = "studios", all = TRUE)
beststudior <- na.omit(beststudior)
beststudior <- beststudior%>% select(studios, startyr,rating.x,avg_rating,production.x,ranking)
colnames(beststudior) <- c("studios","startyr","rating","avg_rating", "production","ranking")

```
Plot the racing graph
```{r, warning=FALSE,message=FALSE,echo=FALSE}
#Plot the graph
top21 <- ggplot(beststudior, aes(ranking, group = studios, 
                fill = as.factor(studios), color = as.factor(studios))) +
  geom_tile(aes(y = rating,
                height = rating,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(studios, " ")), vjust = 0.5, hjust = 0.5, size = 6, fontface="bold") +
  geom_text(aes(y=rating,label = round(rating, digits = 1)), colour = "black", hjust=1) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
#reverse display
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
#set up theme i.e. the backgroud of the plot, the grid line etc
   theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=1),
        plot.subtitle=element_text(size=17, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm"),
       plot.tag.position = c (0.2, 0)) 

#animate the graph with label
anim21 = top21 + transition_states(startyr, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Studio average rating change by year : {closest_state}',  
       subtitle  =  "Best Studio racing plot", tag = "Figure6: Best Studio's raced rating change")

anime2.gif <- animate(anim21, nframes = 150, fps = 2.5, width = 1000, height = 1200)
anime2.gif
```

This plot shows the rate racing between the best studio each year.









