--- 
title: "PSY6422 Project"
subtitle: 'Prolific anime studios prodction and rating'
author: "Halleyson Li"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document: 
  latex_engine: xelatex
biblio-style: apalike
link-citations: yes
linkcolor: blue
frontsize: 12pt
site: bookdown::bookdown_site
knit: "bookdown::render_book"
---

# Overview {-}

Placeholder


## Project motivation
## Project Aims
## Package requirement

<!--chapter:end:index.Rmd-->

---
output:
  pdf_document: default
  html_document: default
---
# Understanding the data

First let us load the data, a quick way to do is simply click the raw data folder from the files section and import.
Another way is by code shows as below: 
```{r, message=FALSE}
library(readr)
anime <- read_csv("raw data/anime.csv")
head(anime)
```

```{r, message=FALSE, results='hide'}
library(tidyverse)
library(ggplot2)
glimpse(anime)

   
summary(anime$votes)

class(anime$votes)

#change all [] to NA
is.na(anime) <- anime == "[]"

#set new data frame to keep the original 
anime1 <- anime

summary(anime$startYr)

#removing special character
gsub("'", "", anime1$studios)
gsub("\\[", "", anime1$studios)

gsub("\\]", "", anime1$studios)


#Froming a table of studio and the amount of production
studio <- aggregate(anime$studios, by = list(anime$studios), FUN = length)
colnames(studio) <- c("studios", "production")

#set Na to 0
anime1$rating[is.na(anime1$rating)] <- 0

anime1$studios[is.na(anime1$studios)] <- 0

# create overall average rating of each studio

studiorate <- aggregate(anime1[, 17], list(anime1$studios), mean)
colnames(studiorate) <- c("studios", "rating")


#merge two table
studioall <- merge(studio,studiorate, by = "studios", all = TRUE)

#only keep top 50 production studios
library(data.table)
studiotop50 <- data.table(studioall, key = "production")
studiotop50 <- studiotop50 %>% 
  arrange(desc(production)) %>% 
  slice (1:50)

  

```


```{r, fig.width= 14, fig.height=10}
studio1959_2020 <- 
  ggplot(data = studiotop50, mapping =  aes(x = production,
                                                y = reorder (studios, production))) + 
  geom_point(aes(size = rating, colour = rating, check_overlap = TRUE)) + 
  geom_text(aes(label = sprintf("%.2f",rating),hjust = -0.5))
                                                                                 
plot <- studio1959_2020 + scale_x_discrete(guide = guide_axis(n.dodge = 5)) +
  scale_x_continuous("production")
  


print(plot)

```


```{r, fig.width= 14, fig.height=10}
studio1959_2020 <- 
  ggplot(data = studiotop50, mapping =  aes(x = rating,
                                                y = reorder (studios, rating))) + 
  geom_point(aes(size = production, colour = rating, check_overlap = TRUE)) + 
  geom_text(aes(label = production),hjust = -0.5) +
  geom_text(aes(label = sprintf("%.2f",rating),hjust = +1.5))
                                                                                 
plot1 <- studio1959_2020 + scale_x_discrete(guide = guide_axis(n.dodge = 5)) +
  scale_x_continuous("rating")
  


print(plot1)

```


Since the first recorded studio starting at 1958, thus

```{r, message=FALSE, results='hide'}

summary(studiotop50$rating)


studiotop37r <- studiotop50 %>% 
  arrange(desc(rating)) %>% 
##after looking at the code, find out how many is below the 2.75 lower quartile
  slice (1:37)

selectstudio <- anime1 %>% select(title, startYr, studios, rating)

selectstudioall <- merge(studiotop37r, selectstudio,by = "studios", all = TRUE)


selectstudioclean <- na.omit(selectstudioall)

colnames(selectstudioclean) <- c("studios", "production","avg_rating","title","startyr","rating")

newavg <- selectstudioclean %>% select(studios, rating, production, avg_rating,startyr)
newavg1 <- aggregate(newavg[, 2:4], list(newavg$studios, newavg$startyr), mean)
colnames(newavg1) <- c("studios","startyr","rating", "production","avg_rating")



```

```{r, fig.show='animate'}

summary(selectstudioclean)


library(gganimate)


library(av)


#create ranking list
newavg2 <- newavg1 %>% group_by(startyr)%>% 
  arrange(startyr, - rating)%>% 
  mutate(ranking = 1:n())

#Drop row that the year is above 2020.

newavg2 <-newavg2 [!(newavg2$startyr == "2021"|newavg2$startyr == "2022"),]


top1 <- ggplot(newavg2, aes(ranking, group = studios, 
                fill = as.factor(studios), color = as.factor(studios))) +
  geom_tile(aes(y = rating,
                height = rating,
                width = 0.9), alpha = 0.8, color = NA) +
  geom_text(aes(y = 0, label = paste(studios, " ")), vjust = 0.5, hjust = 1) +
  geom_text(aes(y=rating,label = rating, hjust=1)) +
  coord_flip(clip = "off", expand = FALSE) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_reverse() +
  guides(color = FALSE, fill = FALSE) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
         axis.title.y=element_blank(),
        legend.position="none",
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.grid.major.x = element_line( size=.1, color="grey" ),
        panel.grid.minor.x = element_line( size=.1, color="grey" ),
        plot.title=element_text(size=25, hjust=0.5, face="bold", colour="grey", vjust=-1),
        plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="grey"),
        plot.caption =element_text(size=8, hjust=0.5, face="italic", color="grey"),
        plot.background=element_blank(),
       plot.margin = margin(2,2, 2, 4, "cm")) 

anim = top1 + transition_states(startyr, transition_length = 4, state_length = 1) +
  view_follow(fixed_x = TRUE)  +
  labs(title = 'Studio rating by year : {closest_state}',  
       subtitle  =  "Top 37 Studio")

animate(anim, nframes = 150, fps = 2, width = 600, height = 500 )




topcompany <- ggplot(data=newavg2,aes (x = studios, y = rating, fill = rating))+
  
  geom_bar(stat = 'identity')+ labs (subtitle = '{closest_state}',x = 'studios')+
  geom_text(aes(label=format(round(rating)), y=rating),
            position=position_dodge(1)) + coord_flip()+
  scale_fill_gradient(low = 'red1', high = 'green1')+
  scale_y_continuous("rating") + theme_classic()+
  theme(legend.position='none')+
  
  transition_states(states=startyr, transition_length=4, state_length = 1) +
  ease_aes('cubic-in-out') 
  

#nframes = 2 x length of the showing year (startyr) other wise only show 50

animate (topcompany, nframes = 150, fps = 2, width = 600, height = 500)

```














With the use of R

<!--chapter:end:01-Data-cleaning.Rmd-->

# Basic interpretation

This section gives a general view of the data.

<!--chapter:end:02-General-interpretation.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Summary



We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

# Some further thoughts regarding the project {-}

Of course, based on the marking 

<!--chapter:end:06-Further-thoughts.Rmd-->

